Introduction

### 2012-10-25 dissertation/tmpsolutions.tex
headline
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@409 43ef1190-90fd-4dd7-a769-d0121f02b80e
more void solutions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@410 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

>>>>

\subsection{VoID extensions}

@@

However, this isn't a histogram, it merely mentioning the objects that
would most likely be useful. To get a histogram we would need a
similar \rdfterm{void:frequency} attribute and both this and
\rdfterm{void:mostFrequentObjects} would have to accept ordered
lists.

Another option would be to do something like:
\begin{verbatim}
_:foo void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects 
    [
      void:object lang:nb ;
      void:frequency "0.012" .
    ]
].
\end{verbatim}
but this solution would be less general but of similar complexity than
the nested solution above.
